Code used to generate paper results

### 2023-08-21 Paper_code.Rmd
Added numbers to gene function

```{r library, message = FALSE}
library(readxl)
library(readr)
library(CTexploreR)
library(Vennerable)
library(biomaRt)
library(tidyverse)
library(SummarizedExperiment)
library(factoextra)
library(UpSetR)
library(ComplexHeatmap)
library(circlize)
library(SingleCellExperiment)
library(org.Hs.eg.db)
library(clusterProfiler)
library(DOSE)
library(tibble)
library(BiocParallel)
library(patchwork)
library(Biostrings)
```

@@

```{r GO_ORA}
go_ora <- enrichGO(gene = CT_genes$ensembl_gene_id,
                   keyType = "ENSEMBL",
                   OrgDb = org.Hs.eg.db,
                   ont = "all",
                   readable = TRUE)
as_tibble(go_ora)

@@

#load("data_rmd/nonCT_per_gene_CD4_datasets.rda")

>>>>

```{r library, message = FALSE}
library(readxl)
library(readr)
library(CTexploreR)
library(Vennerable)
library(biomaRt)
library(tidyverse)
library(SummarizedExperiment)
library(factoextra)
library(UpSetR)
library(ComplexHeatmap)
library(circlize)
library(SingleCellExperiment)
library(org.Hs.eg.db)
library(clusterProfiler)
library(msigdbr)
library(DOSE)
library(tibble)
library(BiocParallel)
library(patchwork)
library(Biostrings)
```

@@

```{r GO_ORA}

msigdbr(species = "Homo sapiens" , category = "C5") %>% 
  filter(gene_symbol %in% CT_genes$external_gene_name) %>% 
  pull(gene_symbol) %>% 
  unique() %>% 
  length()

msigdbr(species = "Homo sapiens" , category = "H") %>% 
  filter(gene_symbol %in% CT_genes$external_gene_name) %>% 
  pull(gene_symbol) %>% 
  unique() %>% 
  length()

go_ora <- enrichGO(gene = CT_genes$ensembl_gene_id,
                   keyType = "ENSEMBL",
                   OrgDb = org.Hs.eg.db,
                   ont = "all",
                   readable = TRUE)
as_tibble(go_ora)

@@

# load("data_rmd/nonCT_per_gene_CD4_datasets.rda")
